null_model

### 2020-09-09 analysis/ts_null_model.Rmd
Modify to calculate in parallel

  site_samples <- data.frame()
  for (j in 1:n){
    iter_samples <- data.frame()
    for(i in unique(plot_data$year)){
      year_data <- plot_data %>% filter(year == i)
      iter_samples <- rbind(iter_samples, get_samp_species(year_data))
    }
    site_samples <- rbind(site_samples, iter_samples %>% mutate(n = j))
  }
  site_samples %>%
    mutate(plot_id = filter_plot) %>%
    pivot_wider(names_from = samp_species, values_from = samp_abun)
}

#drop trait columns that are the same value for every observation, and therefore providing no additional info
clean_trait_matrix <- function(trait_matrix){
  # uniq_vals <- sapply(trait_matrix, function(x){length(unique(x))}) #get number of unique values of each trait
  # col_names <- names(which(uniq_vals == 1)) #find columns where there is only one value for all observations
  # return(select(trait_matrix, -col_names))
  trait_matrix %>%
  select_if(~ length(unique(.)) > 1) %>% #remove columns that have the same value for all columns
  mutate_at(vars(-id, -ends_with("5cat")), list(~scales::rescale(.,to=c(0, 1)))) %>% #rescale variables
  arrange(id) %>%
  column_to_rownames(var = "id")
}

get_trait_matrix <- function(data, species_list, trait_list){ 
  traits <- data %>%
    filter(id %in% species_list) %>%
    dplyr::select(id, all_of(trait_list)) %>%
    distinct()
}
```

@@

@@

get_plot_FD <- function(data, occ_df, filter_plot, ...) {
  plot_samples <- occ_df %>%
    filter(plot_id == filter_plot)

@@

  trait_mat <- data %>%
    filter(id %in% colnames(sample_species_mat)) %>%
    select(-c(biotimeName, taxa, id_species, plot, year, year_abun, 
              year_biomass, traitName, scientificName, plot_id, study_id)
    ) %>%
    distinct() %>%
    select_if(~ length(unique(na.omit(.))) > 1)  #remove columns that have the same value for all columns

@@

null_FD <- map_dfr(unique(sample_plots$plot_id)[1:3], get_plot_FD, 
                   data = sample_plots, occ_df = sample_occurrence,
                   m = "min", corr = "cailliez")
```

@@

get_parallel_FD <- function(data, group_num){
  group_plots <- plot_sizes %>% filter(group == group_num)
  group_data <- data %>% filter(plot_id %in% group_plots$plot_id)

  future::plan(multiprocess)
  fd <- map_dfr(group_plots$plot_id[1:3], get_plot_FD, 
                   data = group_data, trait_range = 18:65, occ_df = sample_occurrence)
    #future_map(group_plots$plot_id, get_fd_safe, data = group_data)

@@

fd <- map_dfr(1:num_groups, get_parallel_FD, data = data)
```

>>>>

  site_samples <- data.frame()
  for (j in 1:n){
    iter_samples <- data.frame()
    for(i in unique(plot_data$year)){
      year_data <- plot_data %>% filter(year == i)
      iter_samples <- rbind(iter_samples, get_samp_species(year_data))
    }
    site_samples <- rbind(site_samples, iter_samples %>% mutate(n = j))
  }
  site_samples %>%
    mutate(plot_id = filter_plot) %>%
    pivot_wider(names_from = samp_species, values_from = samp_abun)
}
```

@@

trait_data <- biotime_traits %>% 
  select(-c(biotimeName, taxa, id_species, plot, year, year_abun, 
              year_biomass, traitName, scientificName, plot_id, study_id)) %>%
  distinct()

@@

get_plot_FD <- function(traits, occ_df, filter_plot, ...) {
  plot_samples <- occ_df %>%
    filter(plot_id == filter_plot)

@@

  trait_mat <- traits %>%
    filter(id %in% colnames(sample_species_mat)) %>%
    select_if(~ length(unique(na.omit(.))) > 1)  #remove columns that have the same value for all columns

@@

null_FD <- map_dfr(unique(sample_plots$plot_id)[1:3], get_plot_FD, 
                   traits = trait_data, occ_df = sample_occurrence,
                   m = "min", corr = "cailliez")
```

@@

get_parallel_FD <- function(group_num){
  browser()
  group_plots <- plot_sizes %>% filter(group == group_num)
  group_data <- sample_occurrence %>% filter(plot_id %in% group_plots$plot_id)

  future::plan(multiprocess)
  fd <- map_dfr(group_plots$plot_id[1:3], get_plot_FD, 
                   traits = group_trait_data, occ_df = group_data)
    #future_map(group_plots$plot_id, get_fd_safe, data = group_data)

@@

fd <- map_dfr(1:num_groups, get_parallel_FD)
```
